|

### 2023-07-19 paper/dcpo_demsupport.Rmd
update

## Loading replication data
load(here("data", "correct_cls_ajps.rda")) # https://osf.io/52u7n/download
load(here("data", "correct_cls_apsr.rda")) # https://osf.io/cws59/download
load(here("data", "expcor_cls_ajps.rda"))  # https://osf.io/cgxjd/download
load(here("data", "expcor_cls_apsr.rda"))  # https://osf.io/uka5g/download
load(here("data", "exp_claassen_input.rda")) # https://osf.io/fcyn3/download

>>>>

## Loading replication data
# Download from osf if files not present 
# (can also be generated by compiling /data_replication/data_replication.Rmd)
if (!file.exists(here("data",
                      "correct_cls_ajps.rda"))) { 
    osf_retrieve_file("5xyvt") %>% 
        osf_download(here("data"))
}
if (!file.exists(here("data",
                      "correct_cls_apsr.rda"))) { 
    osf_retrieve_file("8xgm4") %>% 
        osf_download(here("data"))
}
if (!file.exists(here("data",
                      "expcor_cls_ajps.rda"))) { 
    osf_retrieve_file("rj9g5") %>% 
        osf_download(here("data"))
}
if (!file.exists(here("data",
                      "expcor_cls_apsr.rda"))) { 
    osf_retrieve_file("bxt7m") %>% 
        osf_download(here("data"))
}

load(here("data", "correct_cls_ajps.rda")) # https://osf.io/52u7n/download
load(here("data", "correct_cls_apsr.rda")) # https://osf.io/cws59/download
load(here("data", "expcor_cls_ajps.rda"))  # https://osf.io/cgxjd/download
load(here("data", "expcor_cls_apsr.rda"))  # https://osf.io/uka5g/download
load(here("data", "exp_claassen_input.rda")) # https://osf.io/fcyn3/download
